Decorrelating Errors in Quantum Gates by Random Gate Synthesis

### 2018-09-25 decorrelation/decorrelation.tex
Minor changes to the example

\section{A Simple Example}
As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations. A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit). In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error. When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random. This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}). In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically. In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:

>>>>

\section{A Simple Example}
As a somewhat trivial example, consider a single-qubit $X_\pi$ gate. We will assume that the control hardware implementing this gate is slightly miscalibrated, leading to an over-rotation by angle $\theta$. The diamond distance between this channel and the ideal implementation is $\theta$. If the gate were repeated $N$ total times, the target qubit would experience an accumulated over-rotation of $N\theta$. As shown in Fig.~\ref{fig:simple_example}, a balanced implementation of this gate may consist of two implimentations: 1) the original $X_\theta = \exp(-i (\pi/2+\theta)\sigma_x)$ and 2) the conjugate $X_\theta^\dagger = \exp(-i (\pi/2+\theta)\sigma_x)$. Each time the gate is required in a quantum circuit, one member of this balanced set is chosen uniformly at random. After $N$ applications of this gate, the mean over-rotation angle is zero, with a standard deviation of $\sqrt{N}\theta$. This is equivalent to the perfect gate followed by a stochastic Pauli $X$ error with rate $\theta^2$. The diamond norm of the channel is $\theta^2$, This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}). In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically. In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:
